---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Belen Karakullukcu"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_orig, aes(x = State, y = Deaths_Black)) + geom_point() + scale_x_discrete(guide = guide_axis(angle = 30))
```


If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "CA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?

It is a little hard to see, but in New York, there is a clear spike in deaths caused by Covid in Black population compared to other states. It is a little hard to read the state labels since they are on top of each other, but I couldn't make the gaps between them bigger.

2. Are there any conclusions you can draw?

In California, from April to January, a case spike has been seen in overall cases. Specifically during the month of January, there is a significant spike in cases in Latinx population compared to other populations in California.

3. What were you not able to do due to not having the R knowledge?

For the first plot, I wanted to average Deaths_Total for each month and then plot that against each state.

4. What other data would be useful to better understand this data?

Gender data might have been a useful addition to understand COVID affected any gender differently in each state or during a specific month period. 
